Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2019-10-09 writing/ehp_abstract.tex
Work on paper, use 34 knot threshold

\noindent \textbf{Background:} Tropical cyclones bring severe impacts to
\ac{US} communities, including substantial human health risks, from hazards
that include wind, rain, flooding, and tornadoes. However, studies quantifying
tropical cyclone risks and impacts vary widely in how they classify exposure to
tropical cyclones, using various hazard-based metrics and, in some cases, using
distance from the storm track as a surrogate. \\ 
\textbf{Objectives:} (1)~Investigate how well county-level assessments of
tropical cyclone exposure agree when based on distance versus hazard-based
measurements, as well as among assessments based on different hazard
measurements, and (2)~provide software to improve tropical cyclone exposure
assessment for health-related research. \\ 
\textbf{Methods:} We measured county-level exposure to tropical cyclones in the
\ac{US} based on distance from the storm track, maximum sustained wind,
rainfall, flooding, and tornadoes for all land-falling or near-land Atlantic
basin storms, for~1996\,--\,2011 for all metrics and up to~1988\,--\,2015 for
specific metrics. We quantified how well county-level exposure assessment
agreed for all pairwise combinations of metrics.\\ 
\textbf{Results:} In most of the storms investigated, agreement in county-level
exposure assessment was at best moderate, and often poor, when using distance
compared with four hazard-based measurements. There was also substantial
disagreement in exposure assessment based on all pairwise combinations of the
four hazard-based measurements. There were geographic patterns in exposures
based on these metrics, with most wind-based exposures near the coast, flood-
and rain-based exposures extending to inland and northern counties, and
tornado-based exposures in southern counties. \\ 
\textbf{Discussion:} Our results suggest that when impact studies use distance
as a surrogate for tropical cyclone exposure, or use one hazard-based metric
when the impact is partly or fully caused by a different hazard, the study will
be prone to exposure misclassification.  To facilitate future research, we make
this multi-hazard storm exposure data available through open-source software. 
\end{abstract}

>>>>

\noindent \textbf{Background:} Tropical cyclones bring severe impacts to
	\ac{US} communities, including substantial human health risks, from
	hazards that include wind, rain, flooding, and tornadoes. However, 
	it is difficult to conduct multi-year, multi-storm epidemologic 
	studies without storm hazard datasets that can easily be linked to 
	human health data. Further, while some storm exposure metrics are
	straightforward to measure (e.g., distance from a community to a 
	storm's track), they may poorly capture exposure to storm hazards. \\ 
\textbf{Objectives:} (1)~Provide an open-source dataset to improve tropical
	cyclone exposure assessment for health-related research and
	(2)~investigate agreement between county-level assessments of tropical cyclone
	exposure when based on different storm hazards, to clarify 
	risk of exposure misclassification in epidemiologic studies. \\ 
\textbf{Methods:} We created an open-source dataset with county-level data on
	exposure to tropical cyclones in the \ac{US}. The dataset includes
	measures of distance from the storm track, maximum sustained wind,
	rainfall, flooding, and tornadoes for all land-falling or near-land
	Atlantic basin storms over multiple years (1996\,--\,2011 for all
	metrics, up to~1988\,--\,2015 for specific metrics). [Validation] We measured
	agreement in county-level exposure assessment for all pairwise
	combinations of these metrics. \\ 
\textbf{Results:} We created an open-source dataset ... 
	[Most data agreed well. Flooding is hard to measure.]
	In most of the storms investigated, agreement in county-level
	exposure assessment was at best moderate, and often poor, when using
	distance compared with four hazard-based measurements. There was also
	substantial disagreement in exposure assessment based on all pairwise
	combinations of the four hazard-based measurements. There were
	geographic patterns in exposures based on these metrics, with most
	wind-based exposures near the coast, flood- and rain-based exposures
	extending to inland and northern counties, and tornado-based exposures
	in southern counties. \\ 
\textbf{Discussion:} Our results provide a multi-hazard dataset that can be
	leveraged for epidemiologic research on tropical cyclones.  Further,
	our results suggest that when epidemiologic studies use distance as a
	surrogate for tropical cyclone exposure, or use one hazard-based metric
	when the impact is partly or fully caused by a different hazard, the
	study will be prone to exposure misclassification.  
\end{abstract}

### 2019-10-09 writing/ehp_discussion.tex
Work on paper, use 34 knot threshold

Tropical cyclones impact public health in many ways, and epidemiological
studies of the health risk and impacts associated with tropical cyclone
exposures could help improve preparedness for and response to future tropical
cyclones.  However, tropical cyclones are multi-hazard events, making it
complicated to measure exposure. Here, we provide open-source county-level data
on multiple storm exposure metrics, and we find that county-level tropical
cyclone exposure assessments vary substantially when using a distance-based
metric versus four hazard-based metrics, as well as among different
hazard-based metrics. Our results can inform exposure assessment for future
county-level studies of the health risks and impacts associated with tropical
cyclones exposures, and the open-source data and software we have created
provides multi-hazard, county-level exposure data for such studies.

@@

In creating this hurricane exposure dataset, we aimed for data that are
available for all eastern \ac{US} counties. In addition to providing tropical
cyclone exposure metrics for individual hazards, this data and its associated
software allow users not only to access measurements for single hazards, but
also to create tropical cyclone exposure profiles based on multiple hazards or
craft exposure indices that combine hazard
metrics~\parencite{chakraborty2005population, peduzzi2009assessing}. This
ability can be critical, as different hazards of tropical cyclones often act
synergistically in causing impacts~\parencite{smith2009}.

\begin{comment}
To assist with future tropical cyclone studies, we created and published open
source software with this dataset and accompanying
tools~\parencite{hurricaneexposuredata, hurricaneexposure}.  Many previous
studies have used geographical information system software (e.g., ArcGIS) to
assess exposure to tropical cyclones in the \ac{US}~\parencite{grabich2016,
zandbergen2009, czajkowski2011, kruk2010}.  Here, we offer methods to map and
output historic exposure to tropical cyclones that does not require the use of
proprietary software but instead uses a package written in the R statistical
programming language~\parencite{R}, which is free and open-source.  Further, by
including measurements of different hazard exposures in each county for each
tropical cyclone, this software allows for the development of more complex
exposure indices or models (e.g., random forests, multivariable generalized
linear models) that incorporate multiple tropical cyclone hazard measurements.  
\end{comment}

We investigated how well these data correspond with data from other available
sources (Figures~\ref{fig:windcomparison}\,--\,\ref{fig:floodcomparison}
and~S6\,--\,7). While generally in agreement with data from other sources,
there are a few caveats that should be considered when applying these data in
future studies. The rainfall data are from re-analysis data are generally
well-correlated with observed ground-based station data, but may sometimes
oversmooth very high rainfall values compared to ground-based observations
(Figure~\ref{fig:raincomparison}). When rainfall data is used to create binary
exposure classifications, this disagreement is unlikely to influence results,
as both data sources agree in identifying these as storms with high rainfall,
but it may be important to consider for cases that include rainfall as a
continuous measurement.

The wind data are based on modeled, rather than observed, values, and while the
modeled wind data generally agree well with post-analysis maximum wind radii
from \ac{HURDAT2}~\parencite{landsea2013} (Figure~\ref{fig:windcomparison}),
there were a few storms where the two datasets did not agree as well ($<$90\%
of counties classified into the same wind categories by the two sources of wind
estimates). These storms were exceptionally large systems for which high winds
persisted well inland from landfall, like Hurricanes Sandy and Ike
(Figures~\ref{fig:windcomparison} and\~S6). Since the wind radii are based on
\ldots, they have [advantages]; their main disadvantages is that they provide
categorical, rather than continuous, estimates of wind speed, and in many cases
researchers might prefer more precise estimates of storm wind speeds. However,
since the wind radii data may be useful in some cases as either a primary
metric or for sensitivity analysis, we have include county-level wind estimates
for each storm based on these wind radii, in addition to the continuous modeled
windspeeds, in the open-source data \cite{hurricaneexposuredata}.

For the flooding events data, we found it often corresponded with measurements
from \ac{US} Geographical Survey streamgages, with flood event listings more
likely during storms which elevated stream flows. However, there are
differences between the two flooding datasets, and these highlight both the
difficulty of measuring flood exposure at the county level and inherent
challenges in using the storm event database for epidemiologic exposure
assessment.  The flood and tornado data came from the \ac{NOAA} Storm Events
database, which, while a widely-used database of events maintained by
\ac{NOAA}, is based on reports, and so may be prone to
underreporting~\parencite{Ashley2008flood, Curran2000}, especially in less
populated areas~\parencite{Witt1998, Ashley2007}, as well as to other reporting
errors.

\begin{comment}
[For discussion?] Based on these results, the two data sources were generally
in agreement, but the analysis highlights the difficulty of assessing
storm-related flooding at a multi-county, multi-year scale, as flooding can be
very localized within a county or can \ldots .   
\end{comment}

While these are important caveats for the data, we selected these data sources
as among the best currently available for measuring each of these hazards at a
multi-county, multi-year scale.

@@

We found geographic patterns in tropical cyclones based on the different
exposure metrics that. These patterns were not unexpected based on what is
known about tropical cyclone hazards, but still highlight variations across
metrics that are critical to consider in designing studies for tropical cyclone
epidemiology, and they demonstrate the need for multi-hazard exposure datasets
for tropical cyclone epidemiology. Wind-based exposures had a strong coastal
pattern, which is consistent with the dramatic decrease in wind intensity that
typically characterizes the landfall of tropical cyclones. Exposures by rain-
and distance-based metrics often extended further inland compared to the
wind-based metric, up to the Appalachian mountains. This agrees with previous
research indicating that the Appalachian mountains' topography both enhances
precipitation during tropical cyclones and provides hydrological conditions for
severe flooding~\parencite{rees2001}.  Almost all tornado-based exposures were
in southern coastal states, echoing previous findings that most noteworthy
tropical cyclone-related tornadoes occur on the right-side of the tropical
cyclone track in Atlantic-basin \ac{US} storms~\parencite{moore2012}.  These
exposure averages are somewhat limited as estimates of long-term frequencies,
as tropical cyclones follow decadal patterns~\parencite{kossin2007more} likely
not adequately captured in the available data. However, exposure assessments
spanning over a century have found similar patterns for distance- and
wind-based metrics~\textcite{zandbergen2009, kruk2010} [double-check that refs
found similar patterns].

\begin{comment}
However, these frequency maps, together with evidence from
specific tropical cyclones (Figures~\ref{fig:ivanexposure}
and~\ref{fig:jaccard}),  do illustrate the potential for strong differences in
spatial patterns in tropical cyclone exposures, depending on which tropical
cyclone hazards are considered.  A few previous studies have sought to
determine county-level exposure to tropical cyclones over multi-year periods,
including~\textcite{zandbergen2009}, which estimated exposure in \ac{US}
counties to all \ac{US} landfalling Atlantic-basin tropical cyclones
between~1851 and~2003, using both a distance-based metric and a metric that
combined distance and windspeed, and~\textcite{kruk2010}, which explored
exposure to hurricane-related winds in the \ac{US}, including inland areas,
for~1900\,--\,2008.  Our results suggest that such exposure assessments may
perform well in capturing some tropical cyclone hazards (e.g., wind), but
likely miss other potentially dangerous tropical cyclone exposures, especially
for hazards that repeatedly threaten northern or inland counties (e.g., rain,
flooding).
\end{comment}

@@

We found that there was typically only moderate or low agreement between
county-level exposure classifications for a tropical cyclone when comparing
different exposure metrics. This suggests that the use of one of these metrics
as a proxy for all storm-based hazards in epidemiological research would often
be problematic, introducing exposure misclassification.

\begin{comment}
For example, distance from a tropical cyclone's track is relatively easy to
measure and has been used as an operational metric of exposure to tropical
cyclones in previous large-scale studies (examples include ...). Since distance
itself does not constitute a hazard, distance is meant in these cases as a
surrogate to capture exposure to hazards from the tropical cyclone. However,
here we found that in assessing \ac{US} county-level exposure to tropical
cyclones, distance is, at best, a moderate, and often a very poor, surrogate
for exposure to the specific tropical cyclone hazards of high wind, extreme
rainfall, flooding, and tornadoes (Figure~\ref{fig:jaccard}). Therefore, use of
distance to assess tropical cyclone exposure for impact studies could result in
problematic exposure misclassification, which could mask true associations,
even strong associations, between tropical cyclone exposure and outcomes of
interest in impact studies~\parencite{savitz2016interpreting,
armstrong1998effect}.  
\end{comment}

These findings align with previous results from atmospheric science and related
fields on the characteristics of tropical cyclones. While tropical cyclone
rainfall and windspeed are often well-correlated when the tropical cyclone is
over water~\parencite{cerveny2000}, this relationship often does not remain as
strong once the hurricane has made landfall~\parencite{jiang2008}.  Fast-moving
tropical cyclones bring higher risks of dangerous winds
inland~\parencite{kruk2010}, while slow-moving tropical cyclone are likely to
bring more rain~\parencite{rappaport2000} and cause more damage because of
sustained hazardous conditions~\parencite{rezapour2014}. Further, while the
likelihood and extent of flooding during a tropical cyclone is related to the
tropical cyclone's rainfall, it is also driven by factors like top soil
saturation and the structure of the water basin's drainage
network~\parencite{chen2015, rees2001}.

However, we did find a small set of tropical cyclones for which for which
agreement between metrics were unusually high (e.g., Floyd in~1999, Irene in
2011, Hannah in~2008, Bertha in~1996).  Hurricanes Floyd in~1999 and Irene
in~2011 both made their first \ac{US} landfall in North Carolina at minor
hurricane windspeeds (Category~2 and~1, respectively) and then skimmed the
eastern coast of the \ac{US} north through New England, bringing large rainfall
to much of the eastern coast from North Carolina north and causing extensive
inland flooding in North Carolina (Floyd) and New England
(Irene)~\parencite{avila2013atlantic, lawrence2000atlantic}.  Hurricanes Hannah
in~2008 and Bertha in~1996 followed the eastern coastline north of North
Carolina in a pattern similar to Floyd and Irene. For this set of storms, the
tropical cyclones' persistent proximity to water may have helped maintain wind
speeds in similar patterns to rain and distance exposures, resulting in this
moderate to good agreement among exposure assessments based on different
metrics.

In some cases, exposure misclassification from using one of these exposure
metrics to capture one or more of the other storm hazards may be differential
(i.e., associated with the outcome of interest or with factors associated with
risk of the outcome of interest). For example, tropical cyclone wind exposures
tend to be concentrated in counties near the coast, since most tropical
cyclones rapidly decrease in their sustained windspeed following landfall.
However, tropical cyclone exposures based on distance can extend well inland,
following the tropical cyclone's tracks, but may not adequately capture all
wind-exposed counties near the coast. In this case, if the
etiologically-relevant exposure is high wind but exposure is classified based
on distance, the probability of being misclassified as unexposed would be
higher in coastal counties, while the probability of being misclassified as
exposed would be higher in inland counties. If coastal counties differ from
inland counties in either the outcome of interest or in factors associated with
risk of that outcome, differential exposure misclassification would
exist~\parencite{savitz2016interpreting}. Such differential exposure
misclassification can bias estimates of tropical cyclone effects either towards
the null (estimating a lower or null association compared to the true
association that exists) or away from the null (estimating a larger association
than actually exists)~\parencite{savitz2016interpreting, armstrong1998effect}.

\begin{comment}
The use of a single hazard-based metric (e.g., wind) could cause similar
problems if the impact is driven, at least in part, by a different hazard or by
multiple hazards of the tropical cyclone.
\end{comment}

@@

The conducted case study demonstrates how differences in exposure assessment
across storm exposure metrics can result in differing estimates of expected
physical exposure to tropical cyclones among a population
(Figure~\ref{fig:topelecdependexposure}).  Previous assessments of physical
exposure to tropical cyclones have often focused on solely storm winds and
storm proximity. For example, a global study of exposure and vulnerability to
natural hazards used a combination of windspeed above a certain threshold and
distance from the storm's track to assess
exposure~\parencite{peduzzi2009assessing}. While many storm impacts might be
most strongly linked to wind hazards, there is a growing recognition of the
potential risks of adverse health outcomes and property damage from rain- and
flood-related tropical cyclone hazards in the \ac{US}~\parencite{smith2009}.
Such assessments may underemphasize potentially dangerous exposures to certain
regions of the \ac{US}, particularly inland locations. In fact, based on our
assessment of physical exposures to tropical cyclones among
electricity-dependent Medicare beneficiaries, the highest expected physical
exposure under any metric was measured for Philadelphia County, PA, under the
flood metric (Figure~\ref{fig:topelecdependexposure}).  While this county has a
similar-sized population of electricity-dependent Medicare beneficiaries as
Miami-Dade County, FL (Figure~\ref{fig:topelecdependexposure}), the frequency
of storm-related flood events in this inland county results in a very high
expected physical exposure among this subpopulation, while this county is not
included in the top ten counties for physical exposure based on most of the
other exposure metrics.

@@

Previous research has highlighted the range of impacts that tropical cyclones
can have in \ac{US} communities. However, studies of tropical cyclone exposures
and their impacts have varied widely in how they assess exposure. Here we found
large differences in which counties are exposed to different hazards of
tropical cyclones and that distance is, at best, a moderate, and often a very
poor, surrogate for exposure to the specific tropical cyclone hazards of high
wind, extreme rainfall, flooding, and tornadoes. Use of distance as a surrogate
for any of these hazards could lead to exposure misclassification and, in the
case of tropical cyclone risk and impact studies, including epidemiological
studies, result in biased estimates.  Similarly, if such studies disagree on
their findings, it could result from the often poor agreement between exposure
classifications based on these different metrics, making studies that use
different metrics hard to compare or combine in meta-analyses. Our findings
highlight the importance of clarifying the potential pathway from tropical
cyclone hazards to health impacts when conducting tropical cyclone
epidemiological studies, and then basing exposure assessment on these hazards.
To help, we provide open-source tropical cyclone hazard-related measurements
for a large collection of historical Atlantic-basin cyclones, aggregated at the
county level to align with the spatial scale at which much health-related data
is collected.

>>>>

Epidemiological studies can help characterize which health risks are elevated
during disasters, to what degree, and to whom [Ibrahim editorial; Noji paper].
As a result, these studies help improve disaster preparedness and response
[Noji paper].  However, tropical cyclones are multi-hazard events, making it
complicated to measure exposure.  Here, we provide open-source county-level
data on multiple tropical cyclone exposure metrics and explore limitations in
that data.

Further, we find that county-level tropical cyclone exposure assessments vary
substantially when using different metrics, based either on storm hazards or on
how close the storm's central track came to the community. Our results can
inform exposure assessment for future county-level studies of the health risks
and impacts associated with tropical cyclones exposures, and the open-source
data and software we have created provides multi-hazard, county-level exposure
data for such studies.

@@

We investigated how well the open-source data correspond with
data from other available sources
(Figures~\ref{fig:raincomparison}\,--\,\ref{fig:floodcomparison} and~S2). While
generally in agreement, there are a few caveats that should be considered when
using these data. The rainfall data are generally
well-correlated with ground-based observations, but may sometimes
oversmooth very high rainfall values compared to ground-based observations
(Figure~\ref{fig:raincomparison}). When rainfall data is used to create binary
exposure classifications, this disagreement is unlikely to influence results,
as both data sources agree in identifying these as storms with high rainfall,
but would be important to consider for cases that include rainfall as a
continuous measurement.

The wind data are based on modeled, rather than observed, values, and while the
modeled wind data generally agree well with post-analysis maximum wind radii
from \ac{HURDAT2}~\parencite{landsea2013} (Figure~\ref{fig:windcomparison}),
there were a few storms with some discrepancies. These storms---for example, Hurricane Sandy
in 2012 and Hurricane Ike in 2008---were
unusually large systems for which high winds persisted well inland from
landfall (Figures~\ref{fig:windcomparison}
and~S2).

For the flooding events data, we found that flood event status determined based
on the NOAA Storm Events listings often agreed with measurements from \ac{USGS}
streamgages, with a flood event more likely to be listed if a storm elevated
stream flows in the county (Figure~\ref{fig:floodcomparison}).  However, there
are differences between the two flooding datasets, and these highlight both the
difficulty of measuring flood exposure at the county level and inherent
challenges in using data from a storm event database for epidemiologic exposure
assessment.

For example, there was one storm in Fulton County, GA, for which there was high
streamflow but not an associated flood event listing (Hurricane Ida, 2009).
This storm occurred in November 2009, following a month with historic rainfall
and flooding in Georgia \parencite{shepherd2011overview}.  Therefore, in this
case the flooding associated with Ida was incorporated into an ongoing flood
event listing, with a start date well before the five-day window used to
temporally match storm event listings with tropical cyclone tracks used here.

This disagreement highlights the difficulty of large-scale pairing of storm
tracks with storm event listings---without criteria for temporally matching
event dates to storm tracks, it is likely that many false positives would be
captured, for which the occurrance of a storm in the midst of an ongoing storm
event listing would be improperly attributed to the storm.  However, distance
and time restrictions, like those we used in matching NOAA Storm Event listings
with tropical storm locations and dates, do create the opportunity for
occasional false negatives, as for Hurricane Ida in Fulton County, GA, where a
storm contributes meaningfully to an ongoing event, but the event is not
captured for the storm.

There are further limitations for the flood and tornado data---these data came
from the \ac{NOAA} Storm Events database, which, while a widely-used database
of events maintained by \ac{NOAA}, is based on reports, and so may be prone to
underreporting~\parencite{Ashley2008flood, Curran2000}, especially in
sparsely-populated areas~\parencite{Witt1998, Ashley2007} [Simmons and Sutter
ref], as well as to other reporting errors.

While these are important caveats for the data, we selected these data sources
as among the best currently available for measuring each of these hazards
consistently and comprehensively at a multi-county, multi-year scale. In
addition to providing tropical cyclone exposure metrics for individual hazards,
this dataset and its associated software allow users not only to access
measurements for single hazards, but also to create tropical cyclone exposure
profiles based on multiple hazards or craft exposure indices that combine
hazard metrics~\parencite{chakraborty2005population, peduzzi2009assessing}.
This ability can be critical, as different hazards of tropical cyclones often
act synergistically in causing impacts~\parencite{smith2009}.

@@

We found differences in geographic patterns in average exposures to different
tropical cyclone hazards (Figure~\ref{fig:averageexposure}). These patterns
were not unexpected based on what is known about tropical cyclone hazards, but
still highlight variations that are critical to consider in designing studies
and statistical analysis for tropical cyclone epidemiology. Further, they
demonstrate the need for multi-hazard exposure datasets for tropical cyclone
epidemiology.

Tropical cyclone wind exposures had a strong coastal pattern, which is
consistent with the dramatic decrease in wind intensity that typically
characterizes the landfall of tropical cyclones.  Tropical cyclone rain
exposures tended to extended further inland compared to wind exposures, up to
the Appalachian mountains. This agrees with previous research indicating that
the Appalachian mountains' topography both enhances precipitation during
tropical cyclones and provides hydrological conditions for severe
flooding~\parencite{rees2001}.  Almost all tropical cyclone tornado exposures
were in southern coastal states, consistent with previous evidence that most noteworthy
tropical cyclone-related tornadoes occur on the right-side of the tropical
cyclone track in Atlantic-basin \ac{US} storms~\parencite{moore2012}.  The
exposure averages we calculated are somewhat limited as estimates of long-term
frequencies, as tropical cyclones follow decadal
patterns~\parencite{kossin2007more} likely not adequately captured in the
available data, which covered less than 20 years. However, exposure assessments
spanning over a century have found similar patterns for distance- and
wind-based metrics~\textcite{zandbergen2009, kruk2010} [double-check that refs
found similar patterns].

@@

We found that agreement was typically low across hazard-specific tropical
exposure classifications, and agreement was also typically low between
distance-based tropical cyclone exposure assessment and each of the single
hazard-specific exposures (Figures~\ref{fig:ivanexposure}\,--\,
\ref{fig:jaccard} and S4\,--\,S5). This suggests that the use of a
distance-based metric to assess exposure to any of these hazards, or the use of
measurements from one hazard as a proxy for exposure to any of the other
hazards considered, would often be problematic, introducing exposure
misclassification.

These findings align with previous results from atmospheric science and related
fields on the characteristics of tropical cyclones. While tropical cyclone
rainfall and windspeed can be well-correlated when the tropical cyclone is
over water~\parencite{cerveny2000}, this relationship often weakens once the
hurricane has made landfall~\parencite{jiang2008}.  Fast-moving tropical
cyclones bring higher risks of dangerous winds inland~\parencite{kruk2010},
while slow-moving tropical cyclones are likely to bring more
rain~\parencite{rappaport2000} and cause more damage because of sustained
hazardous conditions~\parencite{rezapour2014}. Further, while the likelihood
and extent of flooding during a tropical cyclone is related to the tropical
cyclone's rainfall, it is also driven by factors like top soil saturation and
the structure of the water basin's drainage network~\parencite{chen2015,
rees2001}.

However, we did find a small set of tropical cyclones for which for which
agreement was high across single-hazard exposure assessments (e.g., Floyd
in~1999, Irene in 2011, Hannah in~2008, Bertha in~1996;
Figure~\ref{fig:jaccard}).  Hurricanes Floyd in~1999 (Figure~S4) and Irene
in~2011 both made their first \ac{US} landfall in North Carolina at minor
hurricane windspeeds (Category~2 and~1, respectively) and then skimmed the
eastern coast of the \ac{US} north through New England, bringing substantial
rainfall to much of the eastern coast from North Carolina north and causing
extensive inland flooding in North Carolina (Floyd) and New England
(Irene)~\parencite{avila2013atlantic, lawrence2000atlantic}.  Hurricanes Hannah
in~2008 and Bertha in~1996 followed the eastern coastline north of North
Carolina in a pattern similar to Floyd and Irene. For this set of storms, the
tropical cyclones' persistent proximity to water may have helped maintain wind
speeds in similar patterns to rain and distance-based exposure assessments,
resulting in more similarities across exposure assessments compared to the
other tropical cyclones we considered.

Since exposure assessments often differ across storm hazards, as well as
between each storm hazard and a distance-based proxy measurement, exposure
misclassification is a potential risk. For some studies, such exposure
misclassification might plausibly be differential (i.e., associated with the
outcome of interest or with factors associated with risk of the outcome of
interest).  For example, tropical cyclone wind exposures tend to be
concentrated in counties near the coast, while tropical cyclone wind exposures
sometimes extend well inland.  If the etiologically-relevant exposure for a
health outcome is extreme rainfall but exposure is classified based on
measurements of wind, the probability of being misclassified as unexposed would
be higher in inland counties, while the probability of being misclassified as
exposed would be higher in coastal counties. If coastal counties differ from
inland counties in either the outcome of interest or in factors associated with
risk of that outcome, exposure misclassification would be
differential~\parencite{savitz2016interpreting}.  Such differential exposure
misclassification could bias estimates of tropical cyclone effects either
towards the null (estimating a lower or null association compared to the true
association that exists) or away from the null (estimating a larger association
than actually exists)~\parencite{savitz2016interpreting, armstrong1998effect}.
[Variation across studies in how exposure is assessed?]

@@

The case study illustrates how differences in exposure assessment
across storm exposure metrics can result in differing conclusions. In this 
case, we found differences in estimates of expected
physical exposure to tropical cyclones among a population when exposure
assessment was based on different storm exposure metrics
(Figure~\ref{fig:topelecdependexposure}).

These results are informative because previous assessments of physical exposure
to tropical cyclones have often concentrated on storm winds and storm
proximity. For example, a global study of exposure and vulnerability to natural
hazards used a combination of windspeed above a certain threshold and distance
from the storm's track to assess exposure~\parencite{peduzzi2009assessing}.
While many storm impacts might be most strongly linked to wind hazards, there
is a growing recognition of the potential risks of adverse health outcomes and
property damage from rain- and flood-related tropical cyclone hazards in the
\ac{US}~\parencite{smith2009}.  Assessments based solely on wind and distance
from the storm track therefore may underemphasize potentially dangerous
exposures to certain regions of the \ac{US}, particularly inland locations.

In fact, based on our assessment of physical exposures to tropical cyclones
among electricity-dependent Medicare beneficiaries, the highest expected
physical exposure under any metric was measured for Philadelphia County, PA,
under the flood metric (Figure~\ref{fig:topelecdependexposure}).  While this
county has a similar-sized population of electricity-dependent Medicare
beneficiaries as Miami-Dade County, FL
(Figure~\ref{fig:topelecdependexposure}), the inland county of Philadelphia has
frequent storm-related flood events, which results in a very high expected
physical exposure among electricity-dependent Medicare beneficiaries in the
county. This exposure is poorly captured by most of the other exposure metrics,
under which Philadelphia County is not included in the top ten counties for
physical exposure~(Figure~\ref{fig:topelecdependexposure}).

@@

Previous research has highlighted the range of impacts that tropical cyclones
can have in \ac{US} communities. However, studies of tropical cyclone exposures
and their impacts have varied widely in how they assess exposure, and there was
not previously a widely available public dataset that captured county-level
exposure to multiple storm hazards. Here we provide open-source tropical
cyclone hazard-related measurements for a large collection of historical
Atlantic-basin cyclones, aggregated at the county level to align with the
spatial scale at which much health-related data is collected.

Further, we investigated agreement in exposure assessment across these metrics
when applied individually. We found large differences in which counties are
exposed to different hazards of tropical cyclones and that distance is, at
best, a moderate, and often a very poor, surrogate for exposure to the specific
tropical cyclone hazards of high wind, extreme rainfall, flooding, and
tornadoes. Use of distance as a surrogate for any of these hazards, or exposure
assessment based on one hazard when the pathway for health impacts is in part
or full through another storm hazard, could lead to exposure misclassification.
In the case of tropical cyclone risk and impact studies, including
epidemiological studies, this would result in biased estimates.  Our findings
highlight the importance of clarifying the potential pathway from tropical
cyclone hazards to health impacts when conducting tropical cyclone
epidemiological studies, and then basing exposure assessment on these hazards.
